---
title: "Lab 6"
author: "Cam Audras"
date: "11/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(broom)
library(equatiomatic)
```

## Rank based test example

Mann-Whitney U (non-parametric alternative to an unpaired 2-sample t-test).

H0: Equal ranks (or medians)
HA: Ranks are not equal (or, medians are not equal)

### Create samples

`set.seed()` to create "pseudorandom, but reproducible samples"

```{r}
set.seed(1414)
gp_1 <- sample.int(20, size = 15, replace = TRUE)

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)
```

Take a quick look at the distributions using `hist()`

```{r}
hist(gp_1)
hist(gp_2)
```

Try a t-test so we can compare the results:

```{r}
ttest <- t.test(gp_1, gp_2)

# If these data were paired, I can just add the argument 'paired = "TRUE"' within thet.test() function
```

This p-value means that IF our samples are drawn from populations with the same mean (i.e., if the null hypothesis is true), there is `r round(ttest$p.value,2)` probability of finding sample means *at least as different* as mine by random chance.

